%The paradigm of software engineering is rapidly shifting towards SOA. Instead of developing everything from the scratch, or using standalone
%libraries, programmers prefer to delegate most of the application functionality to remote web APIs. To facilitate this new development model,
%many service providers are keen on hosting web APIs in cloud environments, which are highly scalable, fault-tolerant deployment targets available under
%well-defined SLAs and pay-as-you-go cost models. As the number of cloud-hosted APIs continues to increase, the need for enforced API governance
%has become an absolute necessity to ensure the quality, reliability and maintainability of web APIs. Existing approaches rely on third party
%API management solutions that operate outside the clouds, which are expensive, tedious to manage and do not provide the required level of
%control and manageability over the APIs deployed in the cloud.

We describe EAGER, a model and a software architecture that facilitates API
governance as a cloud-native feature. EAGER supports comprehensive policy
enforcement, dependency management and a variety of other deployment-time API
governance features. It promotes many software development and maintenance
best practices including versioning, code reuse and retaining API backwards
compatibility. EAGER also includes a language based on Python that enables
creating, debugging and maintaining API policies in a simple and intuitive
manner. EAGER can be built right into the cloud platforms used to host APIs
and automates most governance tasks that would otherwise require custom code
or developer intervention.

%We implement a prototype of EAGER on an open source PaaS cloud to 
%demonstrate its feasibility and effectiveness as a governance engine. 
Our empirical results (gathered using a prototype of EAGER developed for
AppScale)
show that EAGER adds negligibly small overhead to the application deployment process in the cloud, and the overhead grows linearly
with the number of APIs deployed. We also show that EAGER scales well to handle tens of thousands of APIs and hundreds of policies. 
Our future work will consider combined deployment-time and run-time
governance capabilities.
%In this work
%we have also laid the foundation for supporting run-time API governance as a cloud-native feature which we will explore in our future research.
