Our research is heavily motivated by the advances in the areas of SOA governance and service management. Many researchers have highlighted the
importance of these subjects in the past and introduced various models and systems to implement them. Guan et al introduced FASWSM~\cite{1607141} a web service
management framework for application servers. FASWSM uses an adaptation technique that wraps web services in a way so they can be managed by the
underlying application server platform. Wu et al introduced DART-Man~\cite{1504267} a web service management system based on semantic web concepts.
Zhu and Wang proposed a model that uses Hadoop and HBase to store web service metadata and process them to implement a variety of management
functions~\cite{5959326}. Our work deviates from these past approaches since EAGER is strongly focused towards managing APIs in cloud platforms (e.g. PaaS)
and it supports powerful policy enforcement features.

Lin et al proposed a service management system for clouds that monitors all service interactions via special ``hooks'' that are connected to the
cloud-hosted services~\cite{5616981}. These hooks monitor and record service invocations, and also provide an interface so that
the individual service artifacts can be managed remotely. However, this system only supports run-time service management and provides no support for 
deployment-time service management or policy enforcement which are key components of a complete API governance solution. Kikuchi and Aoki~\cite{6525502} proposed
a technique based on model checking to evaluate the operational vulnerabilities and fault propagation patterns in cloud services. However, it does not provide
any active monitoring or enforcement functionality that is required to make it a deployment-time or run-time governance component. Sun et al proposed a reference
architecture for monitoring and managing cloud services~\cite{5579654}. This too lacks deployment-time governance, policy validation support and the ability to 
intercept and act upon API calls which makes it severely short of being a comprehensive governance solution for clouds.

Using policies to govern web service and SOA venues is a well researched idea that's already in widespread use. Researchers have shown that
policies can be used to perform a wide range of tasks related to services such as access control~\cite{4279630,5713420}, fault
diagnosis~\cite{6154236}, customization~\cite{4027138}, composition~\cite{1592403,Erradi:2006:PMS:1515984.1515990} and 
management~\cite{Suleiman:2009:IUM:1564601.1564730,6481237,4028029}. We build on the foundation of these past efforts and attempt
to use policies to govern web APIs deployed in cloud settings. However, we deviate from using a plethora of policy languages, each targeted at achieving 
a specific governance task, and instead strive to implement a single unifying policy language that can be used to specify a wide range of governance
requirements. We also use a simple and intuitive syntax based on the Python programming language, instead of using WS-Policy or any other XML-based
language which we believe are too verbose and tedious to program with.

Peng, Lui and Chen showed that
the major concerns associated with SOA governance involve retaining the high reliability of services, recording how many services
are available on the platform to serve, and making sure all the available services are operating within an acceptable service
level~\cite{4730489}. EAGER attempts to satisfy similar requirements for modern RESTful web APIs deployed in cloud environments. EAGER's policy
validation, dependency management and API change management features are geared at ensuring that deployed services
are highly reliable. Its Metadata Manager and ADP record and keep track of all deployed APIs in a simple but comprehensive manner.
Our future work on run-time governance will focus on ensuring that deployed services are operating under well-defined SLAs 
while providing satisfactory quality of service features
